---
title: "QC-Report"
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
params:
  input: ""
  name: ""
  population: ""
  version: ""
  date: ""
  service: ""
---

```{r setup, echo=FALSE, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(DT)
})
```


```{r echo=FALSE}
data <- read.table(params$input, header = TRUE, sep="\t")
filtered_data <- data %>%
  filter(CHISQ > 300)
```

## Parameters

| Parameter        | Value                       |
|------------------|-----------------------------|
| Job              | `r params$name`            |
| Pipeline Version | `r params$version`          |
| Date             | `r params$date`             |
| Population       | `r params$population    `   |

## Allele-Frequency Correlation


### Uploaded Samples vs. Reference Panel

The plot shows the densities of frequencies falling into each part. The first 5000 points from areas of lowest regional densities will be plotted.

```{r echo=FALSE}

lm_eqn <- function(df){
    m <- lm(REFERENCE_AAF ~ AAF, df)
    eq <- paste('r² =', format(summary(m)$r.squared, digits = 3))
    as.character(as.expression(eq))
}

smoothScatter(data$AAF, data$REFERENCE_AAF, nrpoints = 5000, xlim = c(0, 1),
              xlab = "Ref Allele Frequency (Uploaded Samples)", 
              ylab = "Ref Allele Frequency (Reference Panel)", useRaster = TRUE)
legend("topleft", legend = lm_eqn(data), bty = "n", pch = NA)


```

### Potential Frequency Mismatches

Markers where chisq is greater than 300. 

```{r echo=FALSE}
chisq_length <- nrow(filtered_data)
cat("Total mismatches:", chisq_length, "\n")

if (chisq_length > 0) {
    # Print the first 5000 mismatches
    for (i in 1:min(5000, chisq_length)) {
        cat("Mismatched frequencies for '", filtered_data$ID[i], 
            "' f[", filtered_data$REF[i], ",", filtered_data$ALT[i],"] =
            [", filtered_data$AAF[i], ",", 1 - filtered_data$AAF[i],"] vs
            [", filtered_data$REFERENCE_AAF[i], ",", 1 - filtered_data$REFERENCE_AAF[i],"],
            chisq ", filtered_data$CHISQ[i], "\n", sep = "")
    }
    if (chisq_length > 5000) {
        cat("Report outputs first 5000 mismatches.")
    }
}
```

---

<small>
This report has been created with **`r params$service` (`r params$version`)**.
</small>