---
title: "QC-Report"
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
params:
  maf_file: ""
  validation_report: ""
  qc_report: ""
  name: ""
  allele_frequency_population: ""
  version: ""
  date: ""
  service: ""
---

```{r setup, echo=FALSE, include=FALSE}
suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(knitr)
  library(stringr)
  library(glue)
})
```

| Parameter        | Value                       |
|------------------|-----------------------------|
| Service          | `r params$service`          |
| Job              | `r params$name`             |
| Pipeline Version | `r params$version`          |
| Date             | `r params$date`             |

## Statistics
```{r echo=FALSE, warning=FALSE}

# Define the function
parse_report <- function(file_path) {
  # Read the entire file content
  content <- readLines(file_path)

  # Create a tibble from the log content, filtering out lines starting with :: and those without ':'
  result_df <- tibble(line = content) %>%
    # Filter out lines starting with :: or without a colon (:)
    filter(!str_starts(line, "::") & str_detect(line, ":")) %>%
    # Separate lines into Key and Value based on ':'
    separate(col = line, into = c("Parameter", "Value"), sep = ":", extra = "merge") %>%
    # Trim whitespace from Key and Value
    mutate(across(everything(), ~trimws(.))) %>%
    # Ensure there are no empty Key values and fill missing Values
    filter(!is.na(Parameter) & Parameter != "") %>%
    # Convert the tibble to a data frame
    as.data.frame()
  
   # Return the result as a data frame
  return(result_df)
}

# Define the path to the log file
validation <- parse_report(params$validation_report)
qc <- parse_report(params$qc_report)
kable(rbind(validation,qc))

```

## Allele-Frequency Correlation

### Uploaded Samples vs. Reference Panel

The plot shows the densities of frequencies falling into each part. The first 5000 points from areas of lowest regional densities will be plotted.

```{r echo=FALSE}
if (params$allele_frequency_population != "off") {

    data <- read.table(params$maf_file, header = TRUE, sep="\t")
    
    lm_eqn <- function(df){
        m <- lm(REFERENCE_AAF ~ AAF, df)
        eq <- paste('r2 =', format(summary(m)$r.squared, digits = 3))
        as.character(as.expression(eq))
    }

    smoothScatter(data$AAF, data$REFERENCE_AAF, nrpoints = 5000, xlim = c(0, 1),
                  xlab = "Ref Allele Frequency (Uploaded Samples)", 
                  ylab = "Ref Allele Frequency (Reference Panel)", useRaster = TRUE)
    legend("topleft", legend = lm_eqn(data), bty = "n", pch = NA)
} else {
    cat("Allele Frequency Check is disabled.")
}

```

### Potential Frequency Mismatches

Markers where chisq is greater than 300. 

```{r echo=FALSE}

if (params$allele_frequency_population != "off") {
    
    filtered_data <- data %>%
      filter(CHISQ > 300)

    chisq_length <- nrow(filtered_data)
    if(chisq_length > 0) {
      cat("Total mismatches:", chisq_length, "\n")
    } else {
        cat("No mismatches detected.")
    }

    if (chisq_length > 0) {
        # Print the first 5000 mismatches
        for (i in 1:min(5000, chisq_length)) {
            cat("Mismatched frequencies for '", filtered_data$ID[i], "' f[", filtered_data$REF[i], ",", filtered_data$ALT[i],"] = [", (1-filtered_data$AAF[i]), ",", filtered_data$AAF[i],"] vs [", (1-filtered_data$REFERENCE_AAF[i]), ",", filtered_data$REFERENCE_AAF[i],"], chisq ", filtered_data$CHISQ[i], "\n", sep = "")
        }
        if (chisq_length > 5000) {
            cat("Report outputs only first 5000 mismatches.")
        }
    }
} else {
    cat("Allele Frequency Check is disabled.")
}
```

---

<small>
This report has been created with **`r params$service` (`r params$version`)**.
</small>