---
title: "QC-Report"
output:
  rmdformats::robobook:
    self_contained: true
    thumbnails: false
    lightbox: true
    gallery: false
    highlight: tango
params:
  input: ""
  name: ""
  population: ""
  version: ""
  date: ""
  service: ""
---


```{r echo=FALSE}
data = read.table(params$input, header = FALSE, sep="\t")
data[, 11] <- as.numeric(as.character( data[, 11] ))
miss = data[which(data$V11 > 300),];
```

## Parameters

| Parameter        | Value                       |
|------------------|-----------------------------|
| Job              | `r params$name`            |
| Pipeline Version | `r params$version`          |
| Date             | `r params$date`             |
| Population       | `r params$population    `   |

## Allele-Frequency Correlation


### Uploaded Samples vs. Reference Panel

The plot shows the densities of frequencies falling into each part. The first 5000 points from areas of lowest regional densities will be plotted.

```{r echo=FALSE}

lm_eqn = function(df){
    m = lm(V9 ~ V5, df);
    eq <- paste('r2 =', format(summary(m)$r.squared, digits = 3))
    as.character(as.expression(eq)); 
}

i.s <- smoothScatter(data$V5,data$V9, nrpoints=5000, xlim=c(0,1),xlab="Ref Allele Frequency (Uploaded Samples)", ylab="Ref Allele Frequency (Reference Panel)",useRaster=TRUE)
legend("topleft",legend=lm_eqn(data), bty ="n", pch=NA)

```

### Potential Frequency Mismatches

Markers where chisq is greater than 300. 

```{r echo=FALSE}

 cat("Total mismatches:", length(miss[,11]))


  count = as.integer(0); 
  
if (length(miss[,11]) > 0) {

for (i in 1:length(miss[,11])){

    if(count < 5000){
     count =  count + 1; 
 cat("Mismatched frequencies for '", as.character(miss[i,2]),"' f[", as.character(miss[i,3]) ,",", as.character(miss[i,4]),"] = [",miss[i,5],",",miss[i,6],"] vs [", miss[i,9], ",", miss[i,10], "], chisq ",miss[i,11], "\n",sep=""); 
	} else{
	 cat("Report outputs first 5000 mismatches.");
	 break;
	}
	
}

}

```

---

<small>
This report has been created with **`r params$service`**.
</small>
